Demanding resources: Converging perceptions of challenge and resource characteristics

### 2022-11-11 copy of SIOP2023convergence.Rmd
survey

---
title             : "Demanding resources: Converging characteristics of challenge and resource"
shorttitle        : "Demanding Resources"

@@

@@

### Convergence (same characteristic).

@@

@@

## Maybe do third moderator

>>>>

---
title             : "Demanding resources: Converging perceptions of challenge and resource characteristics"
shorttitle        : "Demanding Resources"

@@

```{r uhoh, fig.cap="Maybe put a hold on this paper as wording of resource and challenge seems very similar"}

library(grid) 
library(magick)
figure <- image_read("uhoh.png")

grid.raster(figure)

see Figure \ref{fig:uhoh}

@@

## Convergence (same characteristic).

@@

### Moderating effects

@@

#### Maybe do third moderator
